### 2014-06-06 Docs/makefiles/makefiles.tex
add versoin # of GNU make
Added some details to the documentation of how Maestro's build system handles dependencies.

The \maestro\ build system uses features of GNU make, which is
typically the default on systems.  The \maestro\ executable is built
in the problem's directory (one of the directories under {\tt
SCIENCE/}, {TEST\_PROBLEMS}, or {UNIT\_TESTS}).  This directory will
contain a makefile, {\tt GNUmakefile}, that includes all the necessary
information to build the executable.

@@

There is no need to explicitly define the dependencies between the
source files for Fortran modules.  The scripts in {\tt
BOXLIB\_HOME/Tools/F\_scripts/} are run at the start of the build
process and parse all the source files and make an explicit list of
the dependency pairs.  This process is defined in {\tt
GMakerules.mak}.

>>>>

The \maestro\ build system uses features of GNU make (version 3.81 or
later), which is typically the default on systems.  The \maestro\
executable is built in the problem's directory (one of the directories
under {\tt SCIENCE/}, {\tt TEST\_PROBLEMS}, or {\tt UNIT\_TESTS}).  This
directory will contain a makefile, {\tt GNUmakefile}, that includes
all the necessary information to build the executable.

@@

There is no need to explicitly define the dependencies between the
source files for Fortran modules.  The scripts in {\tt
BOXLIB\_HOME/Tools/F\_scripts/} are run at the start of the build
process and parse all the source files and make an explicit list of
the dependency pairs.  The execution of these scripts is triggered
by including makefiles of the form {\tt *.depends}.  On a fresh build these
will not exist.  When GNU make cannot find an included makefile it will
first attempt to build it using any relevant targets before issuing an 
error.  The targets for the {\tt *.depends} files contain the recipe for
executing the dependency scripts.  Once these makefiles are built by the
scripts GNU make will then read the dependencies for the current build
from them.  This process is defined in {\tt GMakerules.mak}.
